### 2015-01-21 fundamentals/intro.tex

In addition to providing the fundamental features expected in fuel cycle 
simulators, the \Cyclus paradigm enables essential capabilities that previous 
simulators lack. Critically, its \emph{modular and open architecture}  facilitates 
targeted contribution and collaboration within the nuclear fuel cycle analysis 
community.  Additionally, \emph{agent interchangeability} facilitates direct 
comparison of modeling methodologies. Finally, the flexibility and generality 
of its \emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach} 
enables \Cyclus to be applicable to a broader range of 
fidelities, scales, and applications than to other simulators.

\Cyclus separates the problem of modeling a
physics-dependent supply chain into two distinct components: a simulation kernel and archetypes that
interact with the kernel. The kernel is responsible for the
deployment and interaction logic of entities in the simulation.  Physics calculations and 
customized behaviors are implemented within archetypes. Accordingly, specialists
in a given field can utilize their time and resources in modeling a specific
process associated with the nuclear fuel cycle (e.g., reprocessing and advanced
fuel fabrication), without having to model the entirety of the cycle.

>>>>

In addition to providing the fundamental features expected in fuel cycle 
simulators, the \Cyclus paradigm enables essential capabilities that previous 
simulators lack. Critically, targeted contribution and collaboration within the nuclear fuel cycle analysis 
community are assisted by the \emph{modular and open architecture} of \Cyclus.
Additionally, \Cyclus facilitates direct comparison of modeling methodologies with 
\emph{agent interchangeability}.
Finally, \Cyclus is applicable to a broader range of 
fidelities, scales, and applications than other simulators. 
due to the flexibility and generality 
of its \emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach}

Specialists in a given field should utilize their time and resources in 
modeling the specific processes associated with their area of expertise within 
thenuclear fuel cycle (e.g., reprocessing and advanced
fuel fabrication), without having to model the entirety of the cycle.
\Cyclus supports them by separating the problem of modeling a
physics-dependent supply chain into two distinct components: a simulation kernel and archetypes that
interact with the kernel. The kernel is responsible for the
deployment and interaction logic of entities in the simulation.  Physics calculations and 
customized behaviors are implemented within archetypes.
